### 2022-11-16 austins_sim.rmd
Adding main and austins_sim .rmd files

#doc for Austin to create simulations

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
data <- read_csv("owid-covid-data.csv")
```

```{r}
names(data)
china <- data %>% filter(location == "China", date < "2020-03-15")
```

```{r}
cases <- ggplot(china, aes(x = date, y = total_cases)) + geom_line() + labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
fatalities <- ggplot(china, aes(x = date, y = total_deaths)) + geom_line() + labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
```

```{r}
cases
fatalities
```

```{r}
```

### 2022-11-16 main.rmd

#Main rmd doc for compiling code at the end

```{r}
library(tidyverse)
```

### 2022-11-16 chien_sim.Rmd
create rmd - Chien

##todo

```{r}
library(tidyverse)
library(dplyr)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-11-22 austins_sim.rmd
Added Error Functions to Graphs

@@
 library(dplyr)
+library(pracma)
 ```
@@
 names(data)
-china <- data %>% filter(location == "China", date < "2020-03-15")
+china <- data %>% filter(location == "China", date < "2020-03-20")
+china <- subset(china, select = c(date, total_cases, total_deaths))
+china <- china %>% mutate(days = 1:n())
 ```
@@
 ```{r}
-cases <- ggplot(china, aes(x = date, y = total_cases)) + geom_line() + labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
-fatalities <- ggplot(china, aes(x = date, y = total_deaths)) + geom_line() + labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
+cases <- ggplot(china, aes(x = date, y = total_cases)) + 
+    geom_line() + 
+    labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
+fatalities <- ggplot(china, aes(x = date, y = total_deaths)) + 
+    geom_line() + 
+    labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
 ```
@@
 ```{r}
+x <- 0:60
+func <- function(x) 40000+40000*erf(0.11*x-2)
+func2 <- function(x) 1550+1550*erf(0.08*x-2)
 ```
+
+```{r}
+```
+
+```{r}
+cases_function <- ggplot(china, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=func, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 60, 1)) +
+    labs(title = "Total Cases in China", x = "Days", y = "Total Cases")
+fatalities_function <- ggplot(china, aes(x = days, y = total_deaths)) + 
+    geom_line() + 
+    stat_function(fun=func2, color="#3333e2", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 60, 1)) +
+    labs(title = "Total Deaths in China", x = "Days", y = "Total Deaths")
+```
+
+```{r}
+cases_function
+fatalities_function
+```
+
+```{r}
+```

### 2022-11-28 chien_sim.Rmd
update

@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
 ```{r cars}
-summary(cars)
+covid <- read_csv("owid-covid-data.csv")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r}
+china <- covid %>% 
+  filter(location=="China") %>% 
+  filter(date <= "2020-03-28") %>% 
+  filter(date >= "2020-01-22") %>% 
+  select(date, total_cases, total_deaths) %>% 
+  mutate(days = c(1:67))
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r}
+ggplot() +
+  geom_point(aes(x = date, y = total_cases), data = china)
+#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
+ggplot() +
+  geom_point(aes(x = date, y = total_deaths), data = china)
+#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
+```
+
+```{r}
+x <- 1:67
+ggplot(china,aes(x)) +
+  geom_point(aes(x = days, y = total_cases)) +
+  stat_function(fun=function(x) 40000 + 40000 * erf(0.11*x - 2))
+
+ggplot(china,aes(x)) +
+  geom_point(aes(x = days, y = total_deaths)) +
+  stat_function(fun=function(x) 1600 + 1600 * erf(0.071*x - 1.8))
+```
+
+```{r}
+italy <- covid %>% 
+  filter(location=="Italy") %>% 
+  filter(date <= "2020-04-21") %>%
+  filter(date >= "2020-02-15") %>%
+  select(date, total_cases, total_deaths) %>% 
+  mutate(days = c(1:67))
+italy[45:67,] <- NA
+```
+
+```{r}
+ggplot() +
+  geom_point(aes(x = date, y = total_cases), data = italy)
+#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
+ggplot() +
+  geom_point(aes(x = date, y = total_deaths), data = italy)
+#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
+```
+
+```{r}
+x <- 1:67
+ggplot(italy,aes(x)) +
+  geom_point(aes(x = days, y = total_cases)) +
+  stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))
+
+ggplot(italy,aes(x)) +
+  geom_point(aes(x = days, y = total_deaths)) +
+  stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
+```

### 2022-11-30 austins_sim.rmd
Added Powerpoint rmd and continued analysis

--- 2022-11-16 austins_sim.rmd
@@
 names(data)
-china <- data %>% filter(location == "China", date < "2020-03-15")
+china <- data %>% filter(location == "China", date > "2020-01-22", date < "2020-03-23")
+china <- subset(china, select = c(date, total_cases, total_deaths))
+china <- china %>% mutate(days = 1:n())
 ```
@@
 ```{r}
-cases <- ggplot(china, aes(x = date, y = total_cases)) + geom_line() + labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
-fatalities <- ggplot(china, aes(x = date, y = total_deaths)) + geom_line() + labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
+cases_China <- ggplot(china, aes(x = date, y = total_cases)) + 
+    geom_line() + 
+    labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
+fatalities_China <- ggplot(china, aes(x = date, y = total_deaths)) + 
+    geom_line() + 
+    labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
+print(cases_China)
+print(fatalities_China)
+```
+
+CHINA SIMULATION
+```{r}
+x <- 0:60
+cases_function_china <- function(x) 40000+40000*erf(0.11*x-2)
+fatalities_function_china <- function(x) 1600+1600*erf(0.070*x-1.7)
+
+cases_plot_China <- ggplot(china, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=cases_function_china, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 60, 1)) +
+    labs(title = "Total Cases in China from 1/22/2020 to 3/23/2020 (60 days)", x = "Days", y = "Total Cases")
+fatalities_plot_China <- ggplot(china, aes(x = days, y = total_deaths)) + 
+    geom_line() + 
+    stat_function(fun=fatalities_function_china, color="#3333e2", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 60, 1)) +
+    labs(title = "Total Deaths in China from 1/22/2020 to 3/23/2020 (60 days)", x = "Days", y = "Total Deaths")
+print(cases_plot_China)
+print(fatalities_plot_China)
+```
+
+AUSTRALIA SIMULATION
+```{r}
+australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
+australia <- subset(australia, select = c(date, total_cases, total_deaths))
+australia <- australia %>% mutate(days = 1:n())
 ```
@@
 ```{r}
-cases
-fatalities
+minimizedDays <- 70
+australiaPre <- australia %>% filter(days < minimizedDays)
+cases_Australia <- ggplot(australiaPre, aes(x = date, y = total_cases)) + 
+    geom_line() + 
+    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Cases")
+fatalities_Australia <- ggplot(australiaPre, aes(x = date, y = total_deaths)) +
+    geom_line() + 
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Deaths")
+print(cases_Australia)
+print(fatalities_Australia)
 ```
@@
 ```{r}
+x <- 0:minimizedDays
+cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+
+cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="dotted") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
+    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_line() + 
+    stat_function(fun=fatalities_function_australia, color="#3333e2", size=2, linetype="dotted") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+print(cases_pre_plot_Australia)
+print(fatalities_pre_plot_Australia)
 ```
+
+```{r}
+x <- 0:200
+cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+
+cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 1)) +
+    labs(title = "Total Cases in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_line() + 
+    stat_function(fun=fatalities_function_australia, color="#3333e2", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 1)) +
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+
+print(cases_plot_Australia)
+print(fatalities_plot_Australia)
+```
+
+```{r}
+
+```

### 2022-11-30 main.rmd

@@
-#Main rmd doc for compiling code at the end
+---
+title: "Predicting Covid Data"
+author: Austin Lackey, Chien Lin and Jin Peng
+date: Tuesday, November 6th, 2022
+output: powerpoint_presentation
+---
 
-```{r}
+## The MonteCarlo Study
+
+- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
+- Add more stuff here...
+
+## The Gauss Error function
+
+- The Gauss Error function is widely accepted as a good way to model the spread of covid data, especially in China. By using
+the Gauss Error function, we can predict the spread of covid data in the future for other countries.
+- $a+b*erf(c*x-d)$
+
+# Australia Simulation
+
+## Australia Simulation
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
 library(tidyverse)
+library(dplyr)
+library(pracma)
+data <- read_csv("owid-covid-data.csv")
+australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
+australia <- subset(australia, select = c(date, total_cases, total_deaths))
+australia <- australia %>% mutate(days = 1:n())
+minimizedDays <- 70
+australiaPre <- australia %>% filter(days < minimizedDays)
+cases_Australia <- ggplot(australiaPre, aes(x = date, y = total_cases)) + 
+    geom_line() + 
+    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Cases")
+fatalities_Australia <- ggplot(australiaPre, aes(x = date, y = total_deaths)) +
+    geom_line() + 
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Deaths")
+x <- 0:minimizedDays
+cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="dotted") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
+    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_line() + 
+    stat_function(fun=fatalities_function_australia, color="#3333e2", size=2, linetype="dotted") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+x <- 0:200
+cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_line() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 1)) +
+    labs(title = "Total Cases in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_line() + 
+    stat_function(fun=fatalities_function_australia, color="#3333e2", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 1)) +
+    labs(title = "Total Deaths in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
 ```
+```{r, echo=FALSE}
+# print(cases_Australia)
+# print(fatalities_Australia)
+print(cases_pre_plot_Australia)
+# print(fatalities_pre_plot_Australia)
+# cases_plot_Australia
+# print(fatalities_plot_Australia)
+```
+
+## Australia results
+
+```{r, echo=FALSE}
+# print(cases_Australia)
+# print(fatalities_Australia)
+# print(cases_pre_plot_Australia)
+# print(fatalities_pre_plot_Australia)
+cases_plot_Australia
+# print(fatalities_plot_Australia)
+```
+
+## Italy Simulation
+
+- Add stuff here
+
+## (Fill in Here) Simulation
+
+- Add stuff here
+
+## Works Cited
+
+- Add link to study here
+- Add link to covid data here

### 2022-11-30 jin_sim.Rmd
Adding Jin's simulation file.

---
title: "jin_sim"
output: html_document
date: '2022-11-29'
---

## load library

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(pracma)
```

## read data

```{r}
data <- read.csv("https://raw.githubusercontent.com/stat400-csu/project-5/main/owid-covid-data.csv")
View(data)
```

## extract China data of interest

```{r}
china <- data |>
  filter(location == "China") |>
  filter(date >= "2020-01-22", date <= "2020-03-28") |>
  select(c(date, total_cases, total_deaths)) |>
  mutate(days = 1:n())
head(china)
```

## recreate cumulative number plots of positive cases and fatalities in China

```{r}
positive <- ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases), color = "red") +
  labs(x = "Days", y = "China cumulative number of cases")
positive
fatalities <- ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000)
fatalities
```

## apply nonlinear least square curve fitting to find the targeted guassian error function

```{r}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model1)
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
summary(model2)
```

## superimpose the fitted gaussian error functions to the plots

```{r, warning=FALSE}
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
positive +
  stat_function(fun=fn_model1, color="blue")
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
fatalities +
  stat_function(fun=fn_model2, color="blue")
```

## Monte Carlo simulatioin design

```{r}
set.seed(400)

n <- length(china$days)   # number of observed days
m <- 150    # number of random outcomes
mu <- 1
sig <- 0.01  # the assumed measurement uncertainty is 10%
gau_sample <- matrix(rnorm(n*m, mu, sig), nrow=m, ncol=n)   # matrix of gaussian distribution

# multiply the nominal value with gau_sample for each day
mc_data <- vector()
for (j in 1:n){
  mc_data <- c(mc_data, china$total_cases[j]*gau_sample[,j])
}
mc_data <- matrix(mc_data, nrow=m, ncol=n)  # daily data to obtain 150 series of cases
head(mc_data)
```

## Day of flex (found with the fitted model)

```{r}
# trial 1
try <- mc_data[1,]
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=1:67
tmp <- eval(fn_try_deriv)
min(which(tmp < 0))
```

```{r}
# trial 1
try <- mc_data[1,]
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=1:67
tmp <- eval(fn_try_deriv)
min(which(tmp < 0))
```

## Day of flex (found without the fitted model)

```{r}
flex <- rep(NA, m)

# for each Monte Carlo simulation (m)
for (i in 1:m){
  temp_data <- mc_data[i,]
  num_diff <- 0
  # for each day
  for (j in 1:(n-1)){
    num_diff <- temp_data[j+1] - temp_data[j]
    if (num_diff < 0){
      flex[i] <- j
      break
    }
  }
}

for (i in 1:m){
  temp_data <- mc_data[i,]
  num_diff <- rep(NA,n-1)
  # for each day
  for (j in 1:(n-1)){
    num_diff[j] <- temp_data[j+1] - temp_data[j]
  }
  for (j in 1:(n-1)){
    if (num_diff[j+1] < num_diff[j]){
      flex[i] <- j
      break
    }
  }
}
flex
```

```{r}
temp_data <- mc_data[3,]
  # for each day
for (j in 1:(n-1)){
    num_diff[j] <- temp_data[j+1] - temp_data[j]
}

for (j in 1:(n-1)){
  if (num_diff[j+1] < num_diff[j]){
    print(j)
    break
  }
}
```

### 2022-11-30 jin_sim.Rmd
Added day of flex code.

@@
 mu <- 1
-sig <- 0.01  # the assumed measurement uncertainty is 10%
+sig <- 0.1  # the assumed measurement uncertainty is 10%
 gau_sample <- matrix(rnorm(n*m, mu, sig), nrow=m, ncol=n)   # matrix of gaussian distribution
@@
 
-## Day of flex (found with the fitted model)
+## Day of flex (trial)
 
@@
 # trial 1
-try <- mc_data[1,]
-model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+try <- mc_data[5,]
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
 est_try <- summary(model_try)$parameters
@@
 fn_try_deriv <- D(fn_try_deriv,'x')
-x=1:67
+x=seq(1,67,length.out=6700)
 tmp <- eval(fn_try_deriv)
-min(which(tmp < 0))
+min(x[tmp < 0])
 ```
 
+## Day of flex (complete)
+
 ```{r}
-# trial 1
-try <- mc_data[1,]
-model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+flex_day <- rep(NA, m)
+for (i in 1:m){
+  try <- mc_data[i,]
+  model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
   est_try <- summary(model_try)$parameters
@@
   fn_try_deriv <- D(fn_try_deriv,'x')
-x=1:67
+  x=seq(1,67,length.out=6700)
   tmp <- eval(fn_try_deriv)
-min(which(tmp < 0))
+  flex_day[i] <- min(x[tmp < 0])
+}
+flex_day
 ```
@@
 ```
-
-```{r}
-temp_data <- mc_data[3,]
-  # for each day
-for (j in 1:(n-1)){
-    num_diff[j] <- temp_data[j+1] - temp_data[j]
-}
-
-for (j in 1:(n-1)){
-  if (num_diff[j+1] < num_diff[j]){
-    print(j)
-    break
-  }
-}
-```

### 2022-11-30 jin_sim.Rmd
Added MC (day of flex) plot.

@@
 ```
+## MC (day of flex) plot
+
+```{r}
+ggplot() +
+  geom_point(aes(x=1:m, y=flex_day), color="red")
+
+```
 

### 2022-12-01 jin_sim.Rmd

--- 2022-11-30 jin_sim.Rmd
@@
 }
-flex_day
+
+mean(flex_day)
+sd(flex_day)
+```
+
+## MC (day of flex) plot
+
+```{r}
+ggplot() +
+  geom_point(aes(x=1:m, y=flex_day), color="red") +
+  geom_hline(yintercept=mean(flex_day), color="blue") +
+  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
 ```

### 2022-12-01 main.rmd
Changes to main.rmd

@@
 - $a+b*erf(c*x-d)$
+
+# China Simulation
+
+## China Simulation
+
+- Add stuff here
+
+# Italy Simulation
+
+## Italy Simulation
+
+- Add stuff here
 
@@
 
-## Italy Simulation
-
-- Add stuff here
-
-## (Fill in Here) Simulation
-
-- Add stuff here
-
 ## Works Cited
-
-- Add link to study here
-- Add link to covid data here
+- Link to study:
+- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
+Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
+03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
+- Link to covid data:
+- https://covid19.who.int/

### 2022-12-04 jin_sim.Rmd
Added China analysis to main.

@@
 model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
-summary(model1)
+summary(model1)$parameters
 model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
-summary(model2)
+summary(model2)$parameters
 ```

### 2022-12-04 main.rmd
Added China analysis to main.

@@
 title: "Predicting Covid Data"
-author: Austin Lackey, Chien Lin and Jin Peng
-date: Tuesday, November 6th, 2022
-output: powerpoint_presentation
+author: "Austin Lackey, Chien Lin and Jin Peng"
+date: "Tuesday, November 6th, 2022"
+output:
+  powerpoint_presentation: default
+  beamer_presentation: default
 ---
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# useful libraries
+library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(pracma)
+# read covid data
+data <- read_csv("owid-covid-data.csv")
+```
 
@@
 
-## China Simulation
+## Available Official Data
 
-- Add stuff here
+Cumulative diagnosed positive cases:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
+# extract China data of interest
+china <- data |>
+  filter(location == "China") |>
+  filter(date >= "2020-01-22", date <= "2020-03-28") |>
+  select(c(date, total_cases, total_deaths)) |>
+  mutate(days = 1:n())
+
+# recreate plots
+positive <- ggplot(data = china) +
+  geom_point(aes(x = days, y = total_cases), color = "red") +
+  labs(x = "Days", y = "China cumulative number of cases")
+positive
+```
+
+## Available Official Data
+
+Cumulative fatalities:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
+fatalities <- ggplot(data = china) +
+  geom_point(aes(x = days, y = total_deaths), color = "red") +
+  labs(x = "Days", y = "China cumulative number of fatalities") +
+  ylim(0,5000)
+fatalities
+```
+
+## Fit by the Gauss Error Function
+
+Apply $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.
+
+```{r, include=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+```
+
+```{r, message=FALSE, warning=FALSE}
+model <- nls(total_cases ~ gauss_fn(days,a,b,c,d), 
+             data=china, 
+             start=list(a=10000,b=10000,c=0.1,d=1))
+```
+
+## Fit by the Gauss Error Function
+
+Fit of cumulative diagnosed positive cases:
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+summary(model1)$parameters
+fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
+positive + stat_function(fun=fn_model1, color="blue")
+```
+
+## Fit by the Gauss Error Function
+
+Fit of cumulative fatalities:
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+#summary(model2)$parameters
+fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
+fatalities +
+  stat_function(fun=fn_model2, color="blue")
+```
 

### 2022-12-04 chien_sim.Rmd
update itlay

@@
 ```{r}
+set.seed(400)
 library(tidyverse)
@@
 ```{r cars}
-covid <- read_csv("owid-covid-data.csv")
+data <- read_csv("owid-covid-data.csv")
 ```
@@
 ```{r}
-china <- covid %>% 
+china <- data %>% 
   filter(location=="China") %>% 
@@
 ```{r}
-italy <- covid %>% 
+italy <- data %>% 
   filter(location=="Italy") %>% 
@@
 ```
+
+```{r}
+italy = italy[1:44,]
+n <- 44 # number of observed days
+m <- 150 # number of random outcomes
+
+# the Gaussian distribution (Normal) with mean = 1 and sigma = 0.1
+mu <- 1
+sig <- 0.1 # Gaussian distributed with a 10% standard deviation
+
+# each number in the matrix is part of a Gaussian distribution
+df <- matrix(rnorm(n*m, mu, sig), nrow=m, ncol=n)
+
+# multiplied the nominal value of the diagnosed positive cases of the jth day for the 150 numbers of the jth column of the random matrix mentioned above
+mc_data <- vector()
+for (j in 1:n){
+  mc_data <- c(mc_data, italy$total_cases[j]*df[,j])
+}
+
+mc_data <- matrix(mc_data, nrow=m, ncol=n)  # daily data to obtain 150 series of cases
+head(mc_data)
+```

### 2022-12-04 main.rmd
update itlay

@@
 
-## Italy Simulation
+## Plot of Diagnosed Positive Cases
 
-- Add stuff here
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# extract Italy data
+italy <- data %>% 
+  filter(location=="Italy") %>% 
+  filter(date <= "2020-04-21") %>%
+  filter(date >= "2020-02-15") %>%
+  select(date, total_cases, total_deaths) %>% 
+  mutate(days = c(1:67))
+italy[45:67,] <- NA
+
+ggplot() +
+  geom_point(aes(x = date, y = total_cases), data = italy)
+#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
+```
+
+## Plot of Fatalities
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot() +
+  geom_point(aes(x = date, y = total_deaths), data = italy)
+#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
+```
+
+## Plot of Diagnosed Positive Cases with Gauss Error Function
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+x <- 1:67
+ggplot(italy,aes(x)) +
+  geom_point(aes(x = days, y = total_cases)) +
+  stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))
+```
+
+## Plot of Fatalities with Gauss Error Function
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot(italy,aes(x)) +
+  geom_point(aes(x = days, y = total_deaths)) +
+  stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
+```
 

### 2022-12-05 main.rmd
update intro and slides for mc results

@@
 
-## The MonteCarlo Study
+## Introduction
 
-- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
-- Add more stuff here...
+- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
+- They have then use the function to approximate the number of cumulative positive cases in Italy
+- Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
+- This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
 
@@
 - $a+b*erf(c*x-d)$
+
+## Overview of the Monte Carlo Simulation
+
+- add more...
 
@@
 
+# Monte Carlo Simulations
+
+## China
+
+## Italy
+
+## Australia
+
 ## Works Cited

### 2022-12-05 jin_sim.Rmd
Added introduction and peak day of China.

@@
 ```{r}
-data <- read.csv("https://raw.githubusercontent.com/stat400-csu/project-5/main/owid-covid-data.csv")
+data <- read.csv("owid-covid-data.csv")
 View(data)
@@
 mc_data <- matrix(mc_data, nrow=m, ncol=n)  # daily data to obtain 150 series of cases
-head(mc_data)
+```
+
+```{r}
+# multiply the nominal value with gau_sample for each day
+mc_data_fa <- vector()
+for (j in 1:n){
+  mc_data_fa <- c(mc_data_fa, china$total_deaths[j]*gau_sample[,j])
+}
+mc_data_fa <- matrix(mc_data_fa, nrow=m, ncol=n)  # daily data to obtain 150 series of cases
 ```
@@
 
+```{r}
+flex_day_fa <- rep(NA, m)
+for (i in 1:m){
+  try <- mc_data_fa[i,]
+  model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+  est_try <- summary(model_try)$parameters
+  est_try <- est_try[, 1]
+  names(est_try) <- NULL
+  fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+  fn_try_deriv <- D(fn_try_deriv,'x')
+  x=seq(1,67,length.out=6700)
+  tmp <- eval(fn_try_deriv)
+  flex_day_fa[i] <- min(x[tmp < 0])
+}
+
+mean(flex_day_fa)
+sd(flex_day_fa)
+```
+
 ## MC (day of flex) plot
@@
 
-## Day of flex (found without the fitted model)
+```{r}
+ggplot() +
+  geom_point(aes(x=1:m, y=flex_day_fa), color="red") +
+  geom_hline(yintercept=mean(flex_day_fa), color="blue") +
+  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
+```
+
+## Day of flex (no MC)
 
 ```{r}
-flex <- rep(NA, m)
+try <- china$total_cases
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
 
-# for each Monte Carlo simulation (m)
-for (i in 1:m){
-  temp_data <- mc_data[i,]
-  num_diff <- 0
-  # for each day
-  for (j in 1:(n-1)){
-    num_diff <- temp_data[j+1] - temp_data[j]
-    if (num_diff < 0){
-      flex[i] <- j
-      break
-    }
-  }
-}
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+min(x[tmp < 0])
+```
 
-for (i in 1:m){
-  temp_data <- mc_data[i,]
-  num_diff <- rep(NA,n-1)
-  # for each day
-  for (j in 1:(n-1)){
-    num_diff[j] <- temp_data[j+1] - temp_data[j]
-  }
-  for (j in 1:(n-1)){
-    if (num_diff[j+1] < num_diff[j]){
-      flex[i] <- j
-      break
-    }
-  }
-}
-flex
+```{r}
+try <- china$total_deaths
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+min(x[tmp < 0])
 ```
+
+## superimpose the peak day to the plots
+
+```{r, warning=FALSE}
+fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
+positive +
+  stat_function(fun=fn_model1, color="blue") +
+  geom_segment(aes(x = 18.65517, y = 0, xend = 18.65517, yend = china$total_cases[19]), color="blue")
+fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
+fatalities +
+  stat_function(fun=fn_model2, color="blue") +
+  geom_segment(aes(x = 24.74384, y = 0, xend = 24.74384, yend = china$total_deaths[25]), color="blue")
+```

### 2022-12-05 main.rmd
Added introduction and peak day of China.

--- 2022-12-04 main.rmd
@@
 
-## The MonteCarlo Study
+## The Monte Carlo Study
 
@@
 - Add more stuff here...
+
+## Ciufolini and Paolozzi's Study
+
+* Mathematical prediction of the time evolution of the COVID-19 pandemic by a Gauss error function and Monte Carlo simulations:
+  * The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
+  * Predicted the potential number of cases in Italy.
+  * Predicted the day in which the peak of the number of daily cases in Italy occurs.
 
@@
 
-## Available Official Data
-
-Cumulative diagnosed positive cases:
+## Available Official Data (Positive Cases)
 
@@
 positive <- ggplot(data = china) +
-  geom_point(aes(x = days, y = total_cases), color = "red") +
-  labs(x = "Days", y = "China cumulative number of cases")
+  geom_point(aes(x = date, y = total_cases), color = "red") +
+  labs(x = "Date", y = "China cumulative number of cases")
 positive
@@
 
-## Available Official Data
-
-Cumulative fatalities:
+## Available Official Data (Fatalities)
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
-fatalities <- ggplot(data = china) +
-  geom_point(aes(x = days, y = total_deaths), color = "red") +
-  labs(x = "Days", y = "China cumulative number of fatalities") +
+ggplot(data = china) +
+  geom_point(aes(x = date, y = total_deaths), color = "red") +
+  labs(x = "Date", y = "China cumulative number of fatalities") +
   ylim(0,5000)
-fatalities
 ```
@@
 
-## Fit by the Gauss Error Function
+## Fit by the Gauss Error Function and Peak Day (Positive Cases)
 
-Fit of cumulative diagnosed positive cases:
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+try <- china$total_cases
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+peak1 <- min(x[tmp < 0])
+```
 
@@
 model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
-summary(model1)$parameters
+# summary(model1)$parameters
 fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
-positive + stat_function(fun=fn_model1, color="blue")
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_cases), color = "red") +
+  labs(x = "Days", y = "China cumulative number of cases") +
+  stat_function(fun=fn_model1, color="blue") +
+  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]))
 ```
 
-## Fit by the Gauss Error Function
+## Fit by the Gauss Error Function and Peak Day (Fatalities)
 
-Fit of cumulative fatalities:
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+try <- china$total_deaths
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+peak2 <- min(x[tmp < 0])
+```
 
@@
 fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
-fatalities +
-  stat_function(fun=fn_model2, color="blue")
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_deaths), color = "red") +
+  labs(x = "Days", y = "China cumulative number of fatalities") +
+  ylim(0,5000) +
+  stat_function(fun=fn_model2, color="blue") +
+  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]))
 ```

### 2022-12-05 main.rmd
update edits

@@
 
-## The Monte Carlo Study
+## The Monte Carlo Study:
 
-- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
-- Add more stuff here...
+**Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations**
 
-## Ciufolini and Paolozzi's Study
+<br>
+
+*Author: Ignazio Ciufolini, Antonio Paolozzi*
+
+## Introduction : Ciufolini and Paolozzi's Study
+
+* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
+  * They have then use the function to approximate the number of cumulative positive cases in Italy
+  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
+* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
+
+## Cont.
 
@@
 
-## The Gauss Error function
+## Overview of the Monte Carlo Simulation
 
-- The Gauss Error function is widely accepted as a good way to model the spread of covid data, especially in China. By using
-the Gauss Error function, we can predict the spread of covid data in the future for other countries.
-- $a+b*erf(c*x-d)$
+* create a random matrix : m X n
+  * m = number of random outcomes (*chosen to be 150*)
+  * n = number of observed days (*n = 1,...,j*)
+* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
+- add more...
 
@@
   labs(x = "Days", y = "China cumulative number of cases") +
-  stat_function(fun=fn_model1, color="blue") +
-  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]))
+  stat_function(fun=fn_model1) +
+  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]), color="blue")
 ```
@@
   ylim(0,5000) +
-  stat_function(fun=fn_model2, color="blue") +
-  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]))
+  stat_function(fun=fn_model2) +
+  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
 ```
@@
 - https://covid19.who.int/
+- source to find the second derivative of fitted function:
+- https://proofwiki.org/wiki/Derivative_of_Error_Function

### 2022-12-05 austins_sim.rmd
added montecarlo sim

--- 2022-11-16 austins_sim.rmd
@@
 library(dplyr)
+library(pracma)
+library(minpack.lm)
 ```
@@
 
+AUSTRALIA SIMULATION
 ```{r}
-names(data)
-china <- data %>% filter(location == "China", date < "2020-03-15")
+australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
+australia <- subset(australia, select = c(date, total_cases, total_deaths))
+australia <- australia %>% mutate(days = 1:n())
 ```
@@
 ```{r}
-cases <- ggplot(china, aes(x = date, y = total_cases)) + geom_line() + labs(title = "Total Cases in China", x = "Date", y = "Total Cases")
-fatalities <- ggplot(china, aes(x = date, y = total_deaths)) + geom_line() + labs(title = "Total Deaths in China", x = "Date", y = "Total Deaths")
+minimizedDays <- 70
+australiaPre <- australia %>% filter(days < minimizedDays)
+cases_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    labs(title = "Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+print(cases_Australia)
+print(fatalities_Australia)
 ```
@@
 ```{r}
-cases
-fatalities
+x <- 0:minimizedDays
+
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+cf <- summary(nlsLM(total_cases ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=10000,b=500,c=.02,d=1)))$parameters
+ff <- summary(nlsLM(total_deaths ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=100,b=100,c=.01,d=1)))$parameters
+
+cases_function_australia <- function(x) cf[1]+cf[2]*erf(cf[3]*x-cf[4])
+fatalities_function_australia <- function(x) ff[1]+ff[2]*erf(ff[3]*x-ff[4])
+
+cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+print(cases_pre_plot_Australia)
+print(fatalities_pre_plot_Australia)
+```
+
+```{r}
+x <- 0:200
+
+# cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+# fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+
+cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+
+print(cases_plot_Australia)
+print(fatalities_plot_Australia)
+```
+
+```{r}
+#Montecarlo Simulation
+set.seed(400)
+n <- dim(australia)[1]
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+mc_data_ca <- c()
+for (i in 1:n) {
+    mc_data_ca <- c(mc_data_ca, australia$total_cases[i]*gau_sample[,i])
+}
+mc_data_ca <- matrix(mc_data_ca, nrow = m, ncol = n)
+mc_data_fa <- c()
+for (i in 1:n) {
+    mc_data_fa <- c(mc_data_fa, australia$total_deaths[i]*gau_sample[,i])
+}
+mc_data_fa <- matrix(mc_data_fa, nrow = m, ncol = n)
+
+day_of_flex_ca <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_ca[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=15000,b=9000,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_ca[i] <- min(x[temp < 0])
+}
+print(mean(day_of_flex_ca))
+print(sd(day_of_flex_ca))
+```
+
+```{r}
+day_of_flex_fa <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_fa[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=300,b=200,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_fa[i] <- min(x[temp < 0])
+}
+print(mean(day_of_flex_fa))
+print(sd(day_of_flex_fa))
+```
+
+```{r}
+print(fatalities_plot_Australia + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed"))
+print(cases_plot_Australia + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed"))
 ```

### 2022-12-05 main.rmd
added montecarlo sim

@@
 library(pracma)
+library(minpack.lm)
 # read covid data
 data <- read_csv("owid-covid-data.csv")
+knitr::opts_chunk$set(fig.width=12, fig.height=8) 
 ```
 
-## The Monte Carlo Study:
+## Introduction
 
-**Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations**
+- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
+- They then use the function to approximate the number of cumulative positive cases in Italy
+- Then performed 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
+- This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
 
-<br>
-
-*Author: Ignazio Ciufolini, Antonio Paolozzi*
-
-## Introduction : Ciufolini and Paolozzi's Study
-
-* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
-  * They have then use the function to approximate the number of cumulative positive cases in Italy
-  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
-* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
-
-## Cont.
+## Ciufolini and Paolozzi's Study
 
@@
 
-* create a random matrix : m X n
-  * m = number of random outcomes (*chosen to be 150*)
-  * n = number of observed days (*n = 1,...,j*)
-* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
-  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
 - add more...
@@
 
-## Australia Simulation
+## Initial Data for Cases in Australia
+
 ```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-library(tidyverse)
-library(dplyr)
-library(pracma)
-data <- read_csv("owid-covid-data.csv")
 australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
@@
 australiaPre <- australia %>% filter(days < minimizedDays)
-cases_Australia <- ggplot(australiaPre, aes(x = date, y = total_cases)) + 
-    geom_line() + 
-    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Cases")
-fatalities_Australia <- ggplot(australiaPre, aes(x = date, y = total_deaths)) +
-    geom_line() + 
-    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Deaths")
-x <- 0:minimizedDays
-cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
-fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
-cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
-    geom_line() + 
-    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="dotted") +
-    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
-    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
-fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
-    geom_line() + 
-    stat_function(fun=fatalities_function_australia, color="#3333e2", size=2, linetype="dotted") +
-    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
-    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
-x <- 0:200
-cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
-fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
-cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
-    geom_line() + 
-    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
-    scale_x_continuous(breaks = seq(0, 200, 1)) +
-    labs(title = "Total Cases in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
-fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
-    geom_line() + 
-    stat_function(fun=fatalities_function_australia, color="#3333e2", size=1.5) +
-    scale_x_continuous(breaks = seq(0, 200, 1)) +
-    labs(title = "Total Deaths in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
-```
-```{r, echo=FALSE}
-# print(cases_Australia)
-# print(fatalities_Australia)
-print(cases_pre_plot_Australia)
-# print(fatalities_pre_plot_Australia)
-# cases_plot_Australia
-# print(fatalities_plot_Australia)
+cases_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    labs(title = "Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
 ```
 
-## Australia results
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_Australia)
+```
 
-```{r, echo=FALSE}
-# print(cases_Australia)
-# print(fatalities_Australia)
-# print(cases_pre_plot_Australia)
-# print(fatalities_pre_plot_Australia)
-cases_plot_Australia
-# print(fatalities_plot_Australia)
+## Initial Data for Fatalities in Australia
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_Australia)
+```
+
+## Fitting Gauss Error Function to Cases in Australia
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+x <- 0:minimizedDays
+
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+cf <- summary(nlsLM(total_cases ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=10000,b=500,c=.02,d=1)))$parameters
+ff <- summary(nlsLM(total_deaths ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=100,b=100,c=.01,d=1)))$parameters
+
+cases_function_australia <- function(x) cf[1]+cf[2]*erf(cf[3]*x-cf[4])
+fatalities_function_australia <- function(x) ff[1]+ff[2]*erf(ff[3]*x-ff[4])
+
+cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_pre_plot_Australia)
+```
+
+## Fitting Gauss Error Function to Fatalities in Australia
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_pre_plot_Australia)
+```
+
+## Applying the function to the whole cases dataset
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+x <- 0:200
+
+# cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+# fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+
+cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia)
+```
+
+## Applying the function to the whole fatalities dataset
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_plot_Australia)
+```
+
+## Using MonteCarlo Simulation to predict the day of flex
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+#Montecarlo Simulation
+set.seed(400)
+n <- dim(australia)[1]
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+mc_data_ca <- c()
+for (i in 1:n) {
+    mc_data_ca <- c(mc_data_ca, australia$total_cases[i]*gau_sample[,i])
+}
+mc_data_ca <- matrix(mc_data_ca, nrow = m, ncol = n)
+mc_data_fa <- c()
+for (i in 1:n) {
+    mc_data_fa <- c(mc_data_fa, australia$total_deaths[i]*gau_sample[,i])
+}
+mc_data_fa <- matrix(mc_data_fa, nrow = m, ncol = n)
+
+day_of_flex_ca <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_ca[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=15000,b=9000,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_ca[i] <- min(x[temp < 0])
+}
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+day_of_flex_fa <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_fa[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=300,b=200,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_fa[i] <- min(x[temp < 0])
+}
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+print(mean(day_of_flex_fa))
+print(sd(day_of_flex_fa))
+print(mean(day_of_flex_ca))
+print(sd(day_of_flex_ca))
+```
+
+- The mean of the day of flex for cases is 60.22 days and the standard deviation is 0.77 days.
+- The mean of the day of flex for fatalities is 81.4 days and the standard deviation is 0.69 days.
+
+## Applying the day of flex indicator to the data (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed"))
+```
+
+## Applying the day of flex indicator to the data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_plot_Australia + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed"))
 ```
@@
 - https://covid19.who.int/
-- source to find the second derivative of fitted function:
-- https://proofwiki.org/wiki/Derivative_of_Error_Function

### 2022-12-05 main.rmd

@@
 - This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc. 
+=======
+## The Monte Carlo Study:
 
-## Ciufolini and Paolozzi's Study
+**Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations**
+
+<br>
+
+*Author: Ignazio Ciufolini, Antonio Paolozzi*
+
+## Introduction : Ciufolini and Paolozzi's Study
+
+* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
+  * They have then use the function to approximate the number of cumulative positive cases in Italy
+  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
+* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
+
+## Cont.
 
@@
 
+* create a random matrix : m X n
+  * m = number of random outcomes (*chosen to be 150*)
+  * n = number of observed days (*n = 1,...,j*)
+* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
 - add more...

### 2022-12-05 main.rmd
Updated meeting changes

@@
 
-## Introduction
-
-- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
-- They then use the function to approximate the number of cumulative positive cases in Italy
-- Then performed 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
-- This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc. 
-=======
 ## The Monte Carlo Study:
@@
 
-* Mathematical prediction of the time evolution of the COVID-19 pandemic by a Gauss error function and Monte Carlo simulations:
 * The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
@@
 
-# Monte Carlo Simulations
-
-## China
-
-## Italy
-
-## Australia
-
 ## Works Cited

### 2022-12-05 main.rmd
Combined introduction and formatted the plots

@@
 
-## Introduction : Ciufolini and Paolozzi's Study
+## Ciufolini and Paolozzi's Study
 
-* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
-  * They have then use the function to approximate the number of cumulative positive cases in Italy
-  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
-* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
-
-## Cont.
-
-* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
-* Predicted the potential number of cases in Italy.
-* Predicted the day in which the peak of the number of daily cases in Italy occurs.
+* The time evolution of the number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
+* Performed the function on Italy data to predict the potential number of cases.
+* Performed the Monte Carlo Simulations to predict the day in which the peak of the number of daily cases in Italy occurs.
 
@@
 positive <- ggplot(data = china) +
-  geom_point(aes(x = date, y = total_cases), color = "red") +
+  geom_point(aes(x = date, y = total_cases)) +
   labs(x = "Date", y = "China cumulative number of cases")
@@
 ggplot(data = china) +
-  geom_point(aes(x = date, y = total_deaths), color = "red") +
+  geom_point(aes(x = date, y = total_deaths)) +
   labs(x = "Date", y = "China cumulative number of fatalities") +
@@
 ggplot(data = china) +
-  geom_point(aes(x = days, y = total_cases), color = "red") +
+  geom_point(aes(x = days, y = total_cases)) +
   labs(x = "Days", y = "China cumulative number of cases") +
-  stat_function(fun=fn_model1) +
-  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]), color="blue")
+  stat_function(fun=fn_model1, color="#d33636", size=1.5) + 
+  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
 ```
@@
 ggplot(data = china) +
-  geom_point(aes(x = days, y = total_deaths), color = "red") +
+  geom_point(aes(x = days, y = total_deaths)) +
   labs(x = "Days", y = "China cumulative number of fatalities") +
   ylim(0,5000) +
-  stat_function(fun=fn_model2) +
-  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
+  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) + 
+  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
 ```

### 2022-12-05 chien_sim.Rmd
update

--- 2022-11-28 chien_sim.Rmd
@@
 
-```{r cars}
-covid <- read_csv("owid-covid-data.csv")
+```{r}
+data <- read_csv("owid-covid-data.csv")
 ```
@@
 
+## ITALY
+
 ```{r}
-italy <- covid %>% 
+italy <- data %>% 
   filter(location=="Italy") %>% 
@@
   filter(date >= "2020-02-15") %>%
-  select(date, total_cases, total_deaths) %>% 
-  mutate(days = c(1:67))
+  select(date, total_cases, total_deaths) 
 italy[45:67,] <- NA
+italy <- italy %>% mutate(days = c(1:67))
 ```
@@
 ```{r}
-ggplot() +
-  geom_point(aes(x = date, y = total_cases), data = italy)
-#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
-ggplot() +
-  geom_point(aes(x = date, y = total_deaths), data = italy)
-#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
+
 ```
@@
 ```{r}
+# # without nls fxn
+# ggplot(italy,aes(x)) +
+#   geom_point(aes(x = days, y = total_cases)) +
+#   stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))
+# 
+# ggplot(italy,aes(x)) +
+#   geom_point(aes(x = days, y = total_deaths)) +
+#   stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
+
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+library(minpack.lm)
 x <- 1:67
-ggplot(italy,aes(x)) +
-  geom_point(aes(x = days, y = total_cases)) +
-  stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))
 
-ggplot(italy,aes(x)) +
-  geom_point(aes(x = days, y = total_deaths)) +
-  stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
+# with nls fxn
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+
+c <- summary(nlsLM(total_cases~gauss_fn(days,a,b,c,d), data=italy, start=list(a=50000,b=50000,c=.01,d=1)))$parameters
+d <- summary(nlsLM(total_deaths~gauss_fn(days,a,b,c,d), data=italy, start=list(a=10000,b=10000,c=.01,d=1)))$parameters
+
+cf_italy <- function(x) c[1]+c[2]*erf(c[3]*x-c[4])
+df_italy <- function(x) d[1]+d[2]*erf(d[3]*x-d[4])
+
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
+
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
 ```
+
+## montecarlo sim make matrix
+
+```{r}
+n <- 44
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+italy_mod <- italy[1:44,]
+italy_mod[c(1:6),"total_deaths"] = 0
+
+model_ca <- c()
+for (i in 1:n) {
+    model_ca <- c(model_ca, italy_mod$total_cases[i]*gau_sample[,i])
+}
+model_ca <- matrix(model_ca, nrow = m, ncol = n)
+
+model_fa <- c()
+for (i in 1:n) {
+    model_fa <- c(model_fa, italy_mod$total_deaths[i]*gau_sample[,i])
+}
+model_fa <- matrix(model_fa, nrow = m, ncol = n)
+```
+
+## Day of flex (trial)
+
+```{r}
+# trial 1
+test <- model_fa[11,]
+model_try <- nlsLM(test ~ gauss_fn(days,a,b,c,d), 
+                 data=italy_mod, 
+                 start=list(a=50000,b=50000,c=.01,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+# fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+min(x[tmp < 0])
+```
+
+##
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# cases
+flex_ca <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_ca[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=50000,b=50000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_ca[i] <- min(x[tmp < 0])
+}
+mean(flex_ca)
+sd(flex_ca)
+```
+
+```{r}
+# fatalities
+flex_fa <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_fa[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=15000,b=15000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_fa[i] <- min(x[tmp < 0])
+}
+flex_fa <- flex_fa[-c(12,112,124,133)]
+mean(flex_fa)
+sd(flex_fa)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+#output
+print(mean(flex_fa))
+print(sd(flex_fa))
+print(mean(flex_ca))
+print(sd(flex_ca))
+```
+
+```{r}
+#plot
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
+  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")
+
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") + 
+  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
+```

### 2022-12-05 main.rmd
update

--- 2022-12-05 main.rmd
@@
 
-* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
-  * They have then use the function to approximate the number of cumulative positive cases in Italy
-  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
+* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function:  
+$a+b*erf(c*x-d)$.
+* Used the function to approximate the number of cumulative positive cases in Italy
+* Performed a 150 Monte Carlo simulations to predict the day in which the peak of the number of daily cases in Italy occurs.
 * This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
-
-## Cont.
-
-* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
-* Predicted the potential number of cases in Italy.
-* Predicted the day in which the peak of the number of daily cases in Italy occurs.
-
-## Overview of the Monte Carlo Simulation
-
-* create a random matrix : m X n
-  * m = number of random outcomes (*chosen to be 150*)
-  * n = number of observed days (*n = 1,...,j*)
-* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
-  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
-- add more...
 
@@
 
-## Plot of Diagnosed Positive Cases
+## Initial Data for Cases in Italy
 
@@
   filter(date >= "2020-02-15") %>%
-  select(date, total_cases, total_deaths) %>% 
-  mutate(days = c(1:67))
+  select(date, total_cases, total_deaths)
+  #ref: %>% mutate(days = c(1:67))
 italy[45:67,] <- NA
+italy <- italy %>% mutate(days = c(1:67))
 
-ggplot() +
-  geom_point(aes(x = date, y = total_cases), data = italy)
-#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
+#plot
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
 ```
 
-## Plot of Fatalities
+## Initial Data for Fatalities in Italy
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-ggplot() +
-  geom_point(aes(x = date, y = total_deaths), data = italy)
-#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
+#plot
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
 ```
 
-## Plot of Diagnosed Positive Cases with Gauss Error Function
+## Fitting Gauss Error Function to Positive Cases in Italy
 
@@
 x <- 1:67
-ggplot(italy,aes(x)) +
-  geom_point(aes(x = days, y = total_cases)) +
-  stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))
+
+c <- summary(nlsLM(total_cases~gauss_fn(days,a,b,c,d), data=italy, start=list(a=50000,b=50000,c=.01,d=1)))$parameters
+d <- summary(nlsLM(total_deaths~gauss_fn(days,a,b,c,d), data=italy, start=list(a=10000,b=10000,c=.01,d=1)))$parameters
+
+cf_italy <- function(x) c[1]+c[2]*erf(c[3]*x-c[4])
+df_italy <- function(x) d[1]+d[2]*erf(d[3]*x-d[4])
+
+#plot
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
 ```
 
-## Plot of Fatalities with Gauss Error Function
+## Fitting Gauss Error Function to Fatalities in Italy
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-ggplot(italy,aes(x)) +
-  geom_point(aes(x = days, y = total_deaths)) +
-  stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
+#plot
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
+```
+
+## Overview of the Monte Carlo Simulation
+
+* create a random matrix : m X n
+  * m = number of random outcomes (*chosen to be 150*)
+  * n = number of observed days (*n = 1,...,j*)
+* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
+- add more...
+
+## Using MonteCarlo Simulation to predict the day of flex
+
+- The mean of the day of flex for cases is 40.59 days and the standard deviation is 5.222832 days.
+- The mean of the day of flex for fatalities is 43.46 days and the standard deviation is 5.228381 days.
+
+## 150 Monte Carlo simulations plotted
+
+"Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations"
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+n <- 44
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+italy_mod <- italy[1:44,]
+
+model_ca <- c()
+for (i in 1:n) {
+    model_ca <- c(model_ca, italy_mod$total_cases[i]*gau_sample[,i])
+}
+model_ca <- matrix(model_ca, nrow = m, ncol = n)
+
+model_fa <- c()
+for (i in 1:n) {
+    model_fa <- c(model_fa, italy_mod$total_deaths[i]*gau_sample[,i])
+}
+model_fa <- matrix(model_fa, nrow = m, ncol = n)
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# cases
+flex_ca <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_ca[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=50000,b=50000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_ca[i] <- min(x[tmp < 0])
+}
+mean(flex_ca)
+sd(flex_ca)
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot() +
+  geom_point(aes(x=1:m, y=flex_ca), color="red") +
+  geom_hline(yintercept=mean(flex_ca), color="blue") +
+  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
+```
+
+## Applying the day of flex indicator to the plot (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#plot(cs)
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
+  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")
+```
+
+## Applying the day of flex indicator to the plot (Fatalities)
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# fatalities
+flex_fa <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_fa[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=15000,b=15000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_fa[i] <- min(x[tmp < 0])
+}
+flex_fa <- flex_fa[-c(12,112,124,133)]
+mean(flex_fa)
+sd(flex_fa)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#plot(ft)
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() +
+    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") +
+  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
 ```

### 2022-12-05 chien_sim.Rmd
test

@@
 print(mean(flex_fa))
+
 print(sd(flex_fa))

### 2022-12-06 main.rmd
Adjusted introduction and formatted the plots

@@
 
-* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function:  
-$a+b*erf(c*x-d)$.
-* Used the function to approximate the number of cumulative positive cases in Italy
-* Performed a 150 Monte Carlo simulations to predict the day in which the peak of the number of daily cases in Italy occurs.
-* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.
+* The time evolution of he number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
+* Performed the function on Italy data to approximate the number of cases.
+* Performed 150 Monte Carlo simulations to predict the day in which the peak of the number of daily cases in Italy occurs.
 
@@
 ggplot(data = china) +
-  geom_point(aes(x = days, y = total_cases), color = "red") +
+  geom_point(aes(x = days, y = total_cases)) +
   labs(x = "Days", y = "China cumulative number of cases") +
-  stat_function(fun=fn_model1) +
-  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]), color="blue")
+  stat_function(fun=fn_model1, color="#d33636", size=1.5) +
+  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
 ```
@@
   ylim(0,5000) +
-  stat_function(fun=fn_model2) +
-  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
+  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
+  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
 ```

### 2022-12-06 main.rmd
updates slides

--- 2022-12-05 main.rmd
@@
 
-Apply $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.
+Apply an $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.
 
@@
 
-* create a random matrix : m X n
+* Create a random matrix : m X n
   * m = number of random outcomes (*chosen to be 150*)
   * n = number of observed days (*n = 1,...,j*)
-* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
   * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
-- add more...
+- Add more...
 
@@
 
-"Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations"
+- Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations
 
@@
 
-## Applying the function to the whole cases dataset
-
 ```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(cases_plot_Australia)
+## Applying the function to the future cases dataset
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+cases_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Extrapolating Future Case Data with Gauss Error Function", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Extrapolating Future Fatality Data with Gauss Error Function", x = "Days", y = "Total Deaths")
 ```
 
-## Applying the function to the whole fatalities dataset
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_future)
+```
+
+## Applying the function to the future fatalities dataset
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(fatalities_plot_Australia)
+print(fatalities_plot_Australia_future)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(cases_plot_Australia + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed"))
+print(cases_plot_Australia_future + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") + labs(title="Day of flex indicator for cases (60 days after)"))
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(fatalities_plot_Australia + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed"))
+print(fatalities_plot_Australia_future + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + labs(title="Day of flex indicator for fatalities (81 days after)"))
 ```
+
+# Confirming Results with entire dataset
+
+## Entire data (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+cases_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed")
+    labs(title = "Entire Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
+    labs(title = "Entire Fatalities in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_confirm)
+```
+
+## Entire data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_plot_Australia_confirm)
+```
+
+# Interesting Anomaly with United States Data
+
+## All Data (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+# US data
+us <- data %>% filter(location == "United States")
+us <- subset(us, select = c(date, total_cases, total_deaths))
+us <- us %>% mutate(days = 1:n())
+us <- us %>% mutate(year = substr(date, 1, 4))
+us_data_cases <- ggplot(data=us, aes(x=days, y=total_cases, color=year)) + 
+  geom_point() + 
+  labs(title="Total Cases in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
+us_data_deaths <- ggplot(data=us, aes(x=days, y=total_deaths, color=year)) + 
+  geom_point() + 
+  labs(title="Total Deaths in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(us_data_cases)
+```
+
+## All Data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(us_data_deaths)
+```
+
+## Conclusion
 

### 2022-12-06 paper.rmd

---
title: "Paper"
author: "Austin Lackey, Chien Lin and Jin Peng"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Introduction
### Out motivtion for this project is to...

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# useful libraries
library(tidyverse)
library(pracma)
library(minpack.lm)
# read covid data
data <- read_csv("owid-covid-data.csv")
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

```{r}
print(head(data))
```

# Insert More Below....

### 2022-12-06 powerpoint.rmd

--- 2022-12-06 main.rmd
@@
 ---
-title: "Predicting Covid Data"
+title: "Predicting Covid-19 Data"
 author: "Austin Lackey, Chien Lin and Jin Peng"
-date: "Tuesday, November 6th, 2022"
+date: "Tuesday, December 6th, 2022"
 output:
@@
 library(tidyverse)
-library(dplyr)
-library(ggplot2)
 library(pracma)
@@
 
-* The time evolution of he number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
+* The time evolution of the number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
 * Performed the function on Italy data to approximate the number of cases.
@@
 
-* create a random matrix : m X n
+* Create a random matrix : m X n
   * m = number of random outcomes (*chosen to be 150*)
   * n = number of observed days (*n = 1,...,j*)
-* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
   * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
@@
 
-"Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations"
+Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations
 
@@
 
-## Initial Data for Cases in Australia
+## Initial Data for Australia (Cases)
 
@@
 
-## Initial Data for Fatalities in Australia
+## Initial Data for Australia (Fatalities)
 
@@
 
-## Fitting Gauss Error Function to Cases in Australia
+## Fitting a Gauss Error Function to Australia Data (Cases)
 
@@
 
-## Fitting Gauss Error Function to Fatalities in Australia
+## Fitting a Gauss Error Function to Australia Data (Fatalities)
 
@@
 ```
-
-## Applying the function to the whole cases dataset
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(cases_plot_Australia)
+## Applying the function to the future dataset (Cases)
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+cases_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Extrapolating Future Case Data with Gauss Error Function", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Extrapolating Future Fatality Data with Gauss Error Function", x = "Days", y = "Total Deaths")
 ```
 
-## Applying the function to the whole fatalities dataset
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_future)
+```
+
+## Applying the function to the future dataset (Fatalities)
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(fatalities_plot_Australia)
+print(fatalities_plot_Australia_future)
 ```
 
-## Using MonteCarlo Simulation to predict the day of flex
+# MonteCarlo Simulation for Australia's Day of Flex
 
@@
 
+## MonteCarlo Simulation Data (Cases) (150 trials)
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+australiaMCPlot_cases <- ggplot() +
+    geom_point(aes(x=1:m, y=day_of_flex_ca), color="#d33636") +
+    geom_hline(yintercept=mean(day_of_flex_ca), color="#d33636", linetype="dashed", size=2) + 
+    labs(title = "MonteCarlo Simulation for Day of Flex (Cases)", x = "Trial", y = "Day of Flex")
+australiaMCPlot_fatalities <- ggplot() +
+    geom_point(aes(x=1:m, y=day_of_flex_fa), color="#1b95ff") +
+    geom_hline(yintercept=mean(day_of_flex_fa), color="#1b95ff", linetype="dashed", size=2) + 
+    labs(title = "MonteCarlo Simulation for Day of Flex (Fatalities)", x = "Trial", y = "Day of Flex")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(australiaMCPlot_cases)
+```
+
+## MonteCarlo Simulation Data (Fatalities) (150 trials)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(australiaMCPlot_fatalities)
+```
+
+## Using MonteCarlo Simulation to Predict the Day of Flex
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-print(fatalities_plot_Australia + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed"))
+print(fatalities_plot_Australia_future + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + labs(title="Day of flex indicator for fatalities (81 days after)"))
 ```
 
+# Confirming Results with entire dataset
+
+## Entire data (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+cases_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") +
+    labs(title = "Entire Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
+    labs(title = "Entire Fatalities in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_confirm)
+```
+
+## Entire data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(fatalities_plot_Australia_confirm)
+```
+
+# Interesting Anomaly with United States Data
+
+## All United States Data (Cases)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+# US data
+us <- data %>% filter(location == "United States")
+us <- subset(us, select = c(date, total_cases, total_deaths))
+us <- us %>% mutate(days = 1:n())
+us <- us %>% mutate(year = substr(date, 1, 4))
+us_data_cases <- ggplot(data=us, aes(x=days, y=total_cases, color=year)) + 
+  geom_point() + 
+  labs(title="Total Cases in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
+us_data_deaths <- ggplot(data=us, aes(x=days, y=total_deaths, color=year)) + 
+  geom_point() + 
+  labs(title="Total Deaths in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(us_data_cases)
+```
+
+## All United States Data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(us_data_deaths)
+```
+
+## Conclusion
+
+- The day of flex indicator is a good indicator to predict the time of the peak of the pandemic (for most countries).
+- The gauss error function is a good for countries like...
+  - China, Italy and Australia
+- The gauss error function is not a good fit for countries like...
+  - United States
+  - Any other countries who may have different covid restrictions
+- MonteCarlo simulations are neccesary due to the uncertainty of the data.
+
 ## Works Cited
-- Link to study:
+- Link to the study:
   - I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
@@
 03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
-- Link to covid data:
+- Link to the covid data used:
   - https://covid19.who.int/
-- source to find the second derivative of fitted function:
+- Source to find the second derivative of fitted function:
   - https://proofwiki.org/wiki/Derivative_of_Error_Function

### 2022-12-06 powerpoint.rmd

@@
   * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
-- add more...
 

### 2022-12-06 powerpoint.rmd
update pptx and rmd

@@
 ggplot(data = china) +
-  geom_point(aes(x = days, y = total_deaths), color = "red") +
+  geom_point(aes(x = days, y = total_deaths)) +
   labs(x = "Days", y = "China cumulative number of fatalities") +
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(400)
 # extract Italy data
@@
     geom_point() + 
-    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
@@
     geom_point() + 
-    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
@@
   * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
+* Each of the 150 simulations were fitted with the Gauss error function
+* Then determined the date of the flex for each simulation
 
@@
 
-## 150 Monte Carlo simulations plotted
+## MonteCarlo Simulation Data (Cases) (150 trials)
 
@@
 ggplot() +
-  geom_point(aes(x=1:m, y=flex_ca), color="red") +
-  geom_hline(yintercept=mean(flex_ca), color="blue") +
-  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
+    geom_point(aes(x=1:m, y=flex_ca), color="#d33636") +
+    geom_hline(yintercept=mean(flex_ca), color="#d33636", linetype="dashed", size=1.5) + 
+    labs(title = "MonteCarlo Simulation for Day of Flex (Cases)", x = "Trial", y = "Day of Flex")
 ```
@@
     geom_point() + 
-    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
     labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
-  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")
+  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
 ```
 
-## Applying the day of flex indicator to the plot (Fatalities)
+## MonteCarlo Simulation Data (Fatalities) (150 trials)
 
@@
 
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot() +
+    geom_point(aes(x=1:146, y=flex_fa), color="#1b95ff") +
+    geom_hline(yintercept=mean(flex_fa), color="#1b95ff", linetype="dashed", size=1.5) + 
+    labs(title = "MonteCarlo Simulation for Day of Flex (Fatalities)", x = "Trial", y = "Day of Flex")
+```
+
+## Applying the day of flex indicator to the plot (Fatalities)
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
     geom_point() +
-    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
     labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") +
-  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
+  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
 ```

### 2022-12-10 paper.rmd
formatted paper

@@
 ---
-title: "Paper"
+title: "MonteCarlo Simulation's of the Covid-19 Pandemic"
 author: "Austin Lackey, Chien Lin and Jin Peng"
+date: "Tuesday, December 6th, 2022"
 output: 
-  pdf_document: default
-  html_document:
+  pdf_document:
+    toc: TRUE
+    toc_depth: 2
+    number_sections: TRUE
     df_print: paged
+    fig_caption: TRUE
+    highlight: tango
 ---
-
-## Introduction
-### Out motivtion for this project is to...
-
-```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+```{r setup, include=FALSE}
 # useful libraries
@@
 data <- read_csv("owid-covid-data.csv")
-knitr::opts_chunk$set(fig.width=12, fig.height=8) 
+set.seed(420)
 ```
 
-```{r}
-print(head(data))
-```
+# Background and Motivation (Should we do an Abstract?)
 
-# Insert More Below....
+*Insert text here*
+
+## Ciufolini and Paolozzi's MonteCarlo Study
+
+*Insert text here*
+
+# Jin: China
+
+*Insert text here*
+
+# Chien: Italy
+
+*Insert text here*
+
+# Austin: Australia
+
+## United States Anomaly
+
+*Insert text here*
+
+# Simulation Analysis Summary
+
+*Insert text here*
+
+# Potential Improvements
+
+*Insert text here*
+
+# Works Cited
+
+- Link to the study:
+  - I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
+Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
+03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
+- Link to the covid data used:
+  - https://covid19.who.int/
+- Source to find the second derivative of fitted function:
+  - https://proofwiki.org/wiki/Derivative_of_Error_Function

### 2022-12-12 paper.rmd
updated paper

@@
 set.seed(420)
+knitr::opts_chunk$set(fig.width=3, fig.height=3) 
 ```
 
-# Background and Motivation (Should we do an Abstract?)
+# Introduction (Should we do an Abstract?)
 
-*Insert text here*
+## Background
+
+In our MonteCarlo simulation analysis, we fit a gauss-error function over cumulaative Covid-19 data.
+In the study mentioned below, the authors stated that it is widely accepted that China's Covid-19 data follows a gauss-error function. 
+We decided to test this hypothesis by fitting a gauss-error function over the data of China, Italy, and the United States using data from the World Health Organization (WHO).
+We then used the fitted function to predict the time evolution of the Covid-19 Pandemic in each country.
+For context to our project, time evolution is the rate of change of the number of cases over time.
+By fitting a gauss-error function to partial data, we are able to prefict the day of flex point for that given country. 
+Our primary motivation for this project is to see if the gauss-error function is a good fit for various different countries.
 
@@
 
-*Insert text here*
+Our project is an extension and replication of the study done by Ciufolini and Paolozzi. 
+*"Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations"*. 
+The authors of this study used a MonteCarlo simulation to fit a gauss-error function over the data of China and extending it to Italy.
+In their study, it was widely accepted that China's Covid-19 data follows a gauss-error function.
+
+$$Gauss-Error Function =a+b*erf(c*x-d)$$
+
+The authors perfomed a MonteCarlo simulation with 150 replications to approximate the day of flex point for China and Italy.
+The use of the MonteCarlo simulation was crucial to their study's success as reported cases and fatalities can differ up `to 10%` from the actual number of cases and fatalities.
 
@@
 
-## United States Anomaly
+## Fitting a Gauss-Error Function to Australia's Data
 
-*Insert text here*
+We wanted to extend the findings from the study done by Ciufolini and Paolozzi to other countries.
+The first country that we decided to test was Australia.
+Since we have access to all of Australia's data at the time of writing this report, we decided to test the gauss-error function on a subset timeframe of the entire dataset.
+To begin, we limited our data to the timeframe of 6/2/2020 to 8/9/2020 which is 70 days.
+As you can see in Figure A and Figure B, the data begins to follow a gauss-error function shape.
+The days on the x-axis are the number of days following 6/2/2020.
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
+australia <- subset(australia, select = c(date, total_cases, total_deaths))
+australia <- australia %>% mutate(days = 1:n())
+minimizedDays <- 70
+australiaPre <- australia %>% filter(days < minimizedDays)
+cases_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    labs(title = "Figure A: Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    labs(title = "Figure B: Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_Australia)
+print(fatalities_Australia)
+```
+
+In order to fit a gauss-error function to the data, we used the `nlsLM` function from the `minpack.lm` library.
+This allows us to fit a gauss-error function to the data and find the parameters of the function.
+As you can see in Figures C and D, the fitted function follows the data very well.
+One important distinction to note is that the fatalities begin to follow the gauss-error function shape at a later time than the cases.
+This makes sense as death rates begin to increase after the number of cases begin to increase.
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+x <- 0:minimizedDays
+
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+cf <- summary(nlsLM(total_cases ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=10000,b=500,c=.02,d=1)))$parameters
+ff <- summary(nlsLM(total_deaths ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=100,b=100,c=.01,d=1)))$parameters
+
+cases_function_australia <- function(x) cf[1]+cf[2]*erf(cf[3]*x-cf[4])
+fatalities_function_australia <- function(x) ff[1]+ff[2]*erf(ff[3]*x-ff[4])
+
+cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Figure C: Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=2, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
+    labs(title = "Figure D: Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_pre_plot_Australia)
+print(fatalities_pre_plot_Australia)
+```
+
+## Extrapolating the Gauss-Error Function to Australia's Future Data
+
+Once we have a fitted gauss-error function, we can extrapolate the function to the future.
+We decided to extrapolate the function to 200 days which is an increase from China's and Italy's extrapolation. 
+The reasoning for this increase is that it takes longer for the number of cases to increase in Australia than it does in China and Italy.
+We are not quite sure why this is the case, but we believe it is due to the fact that Australia had different restrictions in place than China and Italy.
+As you can see in Figures E and F, the extrapolated function starts to show us an idea of what the future of Australia's data could look like if the current trend continues.
+The first thing we noticed was that the cases were getting close to their expected plateau and the fatalities were just beggining to increase.
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+x <- 0:200
+
+# cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
+# fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
+
+cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) +
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    labs(title = "Total Deaths in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+cases_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Figure E: Extrapolating Future Case Data with Gauss Error Function", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) +
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    xlim(0, 200) +
+    labs(title = "Figure F: Extrapolating Future Fatality Data with Gauss Error Function", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_future)
+print(fatalities_plot_Australia_future)
+```
+
+## MonteCarlo Simulation for Australia's Day of Flex
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+#Montecarlo Simulation
+set.seed(400)
+n <- dim(australia)[1]
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+mc_data_ca <- c()
+for (i in 1:n) {
+    mc_data_ca <- c(mc_data_ca, australia$total_cases[i]*gau_sample[,i])
+}
+mc_data_ca <- matrix(mc_data_ca, nrow = m, ncol = n)
+mc_data_fa <- c()
+for (i in 1:n) {
+    mc_data_fa <- c(mc_data_fa, australia$total_deaths[i]*gau_sample[,i])
+}
+mc_data_fa <- matrix(mc_data_fa, nrow = m, ncol = n)
+
+day_of_flex_ca <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_ca[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=15000,b=9000,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_ca[i] <- min(x[temp < 0])
+}
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+day_of_flex_fa <- rep(NA, m)
+for (i in 1:m) {
+    trial <- mc_data_fa[i,]
+    trial_model <- nlsLM(trial ~ gauss_fn(days,a,b,c,d), data=australia, start=list(a=300,b=200,c=.01,d=1))
+    model_coef <- summary(trial_model)$parameters[, 1]
+    # trial_function <- function(x, coef) {coef[1] + coef[2]*erf(coef[3]*x-coef[4])}
+    gauserr_derivative <- {2/sqrt(pi)*exp(-x^2)}
+    function_trial_derivative <- D(bquote(.(model_coef[2])*2/sqrt(pi)*exp(-(.(model_coef[3])*x-.(model_coef[4]))^2)), 'x')
+    x = seq(1, 200, length.out=6700)
+    temp <- eval(function_trial_derivative)
+    day_of_flex_fa[i] <- min(x[temp < 0])
+}
+```
+
+In order to account for the `10%` variance in the reported data, we need to run a MonteCarlo simulation.
+We decided to run a MonteCarlo simulation with a `150` iterations and a `0.1` standard deviation.
+The reason we chose a `150` iterations is because we wanted to have a large enough sample size to get a good idea of the variance in the data.
+This was also the same values that Ciufolini and Paolozzi used in their paper.
+As you can see in Figures G and H, the MonteCarlo simulation shows us that the variance in the data is not as large as it was for China and Italy.
+We believe this is due to the fact that since Australia required more days to reach their peak, the variance in the data is smaller since `n` is much larger.
+The day of flex for cases in Australia appears to reside around `r round(mean(day_of_flex_ca), 2)` days with a standard deviation of `r round(sd(day_of_flex_ca), 2)` days.
+The day of flex for fatalities in Australia appears to reside around `r round(mean(day_of_flex_fa), 2)` days with a standard deviation of `r round(sd(day_of_flex_fa), 2)` days.
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+australiaMCPlot_cases <- ggplot() +
+    geom_point(aes(x=1:m, y=day_of_flex_ca), color="#d33636") +
+    theme(title =element_text(size=6)) + 
+    geom_hline(yintercept=mean(day_of_flex_ca), color="#d33636", linetype="dashed", size=2) + 
+    labs(title = "Figure G: MonteCarlo Simulation for Day of Flex (Cases)", x = "Trial", y = "Day of Flex")
+australiaMCPlot_fatalities <- ggplot() +
+    geom_point(aes(x=1:m, y=day_of_flex_fa), color="#1b95ff") +
+    theme(title =element_text(size=6)) +
+    geom_hline(yintercept=mean(day_of_flex_fa), color="#1b95ff", linetype="dashed", size=2) + 
+    labs(title = "Figure G: MonteCarlo Simulation for Day of Flex (Fatalities)", x = "Trial", y = "Day of Flex")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(australiaMCPlot_cases)
+print(australiaMCPlot_fatalities)
+```
+
+## Applying the day of flex indicator to the data
+
+As you can see in Figures I and J, the day of flex indicator for cases and fatalities appears to sit right on the midpoint of the projected gauss-curve.
+This is because the day of flex indicator is the point at which the derivative of the gauss-curve is equal to `0`.
+This is when the daily cases and fatalities are at their peak and begin to decline.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_future + 
+  geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") + 
+  labs(title="Figure I: Day of flex indicator for cases (60 days after)") + 
+  theme(title =element_text(size=6)))
+print(fatalities_plot_Australia_future + 
+  geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
+  labs(title="Figure J: Day of flex indicator for fatalities (81 days after)") + 
+  theme(title =element_text(size=6)))
+```
+
+## Confirming Results with entire dataset
+
+In order to confirm our results, we decided to overlay our findings with the entire dataset to see how well our model fits the actual data.
+As you can see in Figures K and L, our model did a decent job of fitting the actual data.
+It appears the model works the best for fatalities but the cases model starts to be a little innacurate once the data starts to plateau.
+Our theory for this inconsistency between fatalities and cases is that it is far easier to report fatalities than it is to report cases.
+It is not often that a person will die from the virus and not be tested or reported.
+However, it is very common for a person to have the virus and not be reported.
+This variance in the data once it begins to plateau could be due to the fact that testing procedures could have changed or the reporting procedures could have changed.
+Since the curve starts to overestimate and then starts to underestimate, Australia could have had a few weeks where they were not doing as much testing, and then they started doing more testing.
+This could explain the variance in the tail of the data.
+Regardless of this variance, our model did a good job at predicting and fitting the day of flex.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+cases_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) + 
+    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") +
+    labs(title = "Figure K: Entire Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+fatalities_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) +
+    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
+    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
+    labs(title = "Figure L: Entire Fatalities in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(cases_plot_Australia_confirm)
+print(fatalities_plot_Australia_confirm)
+```
+
+# United States Anomaly
+
+An interesting anomaly that we found in the data was that the United States had a hard time fitting the gauss-error funciton.
+As you can see in Figures M and N, the United States data does not ever begin to plateau. 
+The data is always at an increasing rate.
+This makes it hard to predict when the day of flex will be.
+We believe that this is due to the fact that the United States had very lax restrictions when compared to other countries.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
+# US data
+us <- data %>% filter(location == "United States")
+us <- subset(us, select = c(date, total_cases, total_deaths))
+us <- us %>% mutate(days = 1:n())
+us <- us %>% mutate(year = substr(date, 1, 4))
+us_data_cases <- ggplot(data=us, aes(x=days, y=total_cases, color=year)) + 
+  geom_point() + 
+  labs(title="Figure M: Total Cases in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
+us_data_deaths <- ggplot(data=us, aes(x=days, y=total_deaths, color=year)) + 
+  geom_point() + 
+  labs(title="Figure N: Total Deaths in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+print(us_data_cases)
+print(us_data_deaths)
+```
 
@@
 
-*Insert text here*
+In our simulation analysis, we found that the day of flex indicator was a good predictor of when the day of flex would be for most countries.
+This model may not be the best model for countries who have different restrictions or have different testing procedures.
 
@@
 
-*Insert text here*
+One idea that comes to mind in terms of improvements for this model is to see if we can account for the changes in testing procedures. 
+This could be done by looking at the data and seeing when the testing procedures changed and then adjusting the model to account for this change.
+Although this would require advanced knowledge of the data as well as policy changes, but it could be a good way to improve the model.
+Another idea is to see if we could find other models that fit countries with laxer restrictions better.
+If they don't follow a gauss-error function, then we could try to explore other models that fit their data better.
 

### 2022-12-14 paper.rmd
updated paper pdf+rmd

@@
 We decided to test this hypothesis by fitting a gauss-error function over the data of China, Italy, and the United States using data from the World Health Organization (WHO).
+
 We then used the fitted function to predict the time evolution of the Covid-19 Pandemic in each country.
 For context to our project, time evolution is the rate of change of the number of cases over time.
-By fitting a gauss-error function to partial data, we are able to prefict the day of flex point for that given country. 
-Our primary motivation for this project is to see if the gauss-error function is a good fit for various different countries.
+By fitting a gauss-error function to partial data, we are able to prefict the day of flex point (which is the day of the highest cases/fatality occurrence) for that given country.
+Our primary motivation for this project is to see if the gauss-error function is a good fit for various different countries and use MonteCarlo simulation to predict for future trends where the data are "unknown".
+
+The results of this study are based on mathematical and statistic approaches alone and do not take into account any of the influential factors such as, stated in the study: number of daily nasopharyngeal swabs, medical, social distancing, virological and epidemiological or models of contamination diffusion.
+Consequently, the accuracy of this study in terms of real world application, may not be too useful.
 
@@
 
-*Insert text here*
+## Preview of the Data
+
+After the Gauss Error function is fitted to the China data, and verified that the function fits well with both the cases data and the fatality data, the study then proceeds to fit the function to the data from Italy.
+
+In this part, we will fit the Gauss Error function to the Italy data and verify if the function is well fitted.
+For MonteCarlo simulation purposes we will only use Italy data from date 2/15/2020 to 3/29/2020, even though data for future dates are available.
+
+First, we will take a look at the data:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+set.seed(400)
+# extract Italy data
+italy <- data %>% 
+  filter(location=="Italy") %>% 
+  filter(date <= "2020-04-21") %>%
+  filter(date >= "2020-02-15") %>%
+  select(date, total_cases, total_deaths)
+  #ref: %>% mutate(days = c(1:67))
+italy[45:67,] <- NA
+italy <- italy %>% mutate(days = c(1:67))
+
+#plot
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure I: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
+#plot
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure II: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
+```
+
+As you can see, the data points already follows a pattern that looks like the cumulative distribution of a Gauss Error function.
+
+## Fitting Gauss Error Function to Italy data
+
+We will verify with the function fitted:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+
+x <- 1:67
+
+c <- summary(nlsLM(total_cases~gauss_fn(days,a,b,c,d), data=italy, start=list(a=50000,b=50000,c=.01,d=1)))$parameters
+d <- summary(nlsLM(total_deaths~gauss_fn(days,a,b,c,d), data=italy, start=list(a=10000,b=10000,c=.01,d=1)))$parameters
+
+cf_italy <- function(x) c[1]+c[2]*erf(c[3]*x-c[4])
+df_italy <- function(x) d[1]+d[2]*erf(d[3]*x-d[4])
+
+#plot
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure III: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
+#plot
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() + 
+    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure IV: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
+```
+
+## Monte Carlo Simulation
+
+The Monte Carlo method we will simulate will be as follows:
+
+* Create a random matrix : m X n
+  * m = number of random outcomes (*chosen to be 150*)
+  * n = number of observed days (*n = 1,...,j*)
+* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
+  * Multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
+* Each of the 150 simulations were fitted with the Gauss error function
+* Then determined the date of the flex for each simulation
+
+Basically, we want to simulate 150 of the function drawn according to the data (which means for different data, the function fitted will have different parameters) with a noise of a Normal random distribution with mean 1 and standard deviation 1.
+
+## MonteCarlo Simulation for Predicting Day of Flex for Italy
+
+Then we run the simulation to get the mean day of the highest case/fatality:
+
+### MonteCarlo Simulation for Cumulative Positive Cases of COVID-19 in Italy
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+n <- 44
+m <- 150
+sigma <- 0.1
+mu <- 1
+gau_sample <- matrix(rnorm(n*m, mean=mu, sd=sigma), nrow = m, ncol = n)
+
+italy_mod <- italy[1:44,]
+
+model_ca <- c()
+for (i in 1:n) {
+    model_ca <- c(model_ca, italy_mod$total_cases[i]*gau_sample[,i])
+}
+model_ca <- matrix(model_ca, nrow = m, ncol = n)
+
+model_fa <- c()
+for (i in 1:n) {
+    model_fa <- c(model_fa, italy_mod$total_deaths[i]*gau_sample[,i])
+}
+model_fa <- matrix(model_fa, nrow = m, ncol = n)
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# cases
+flex_ca <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_ca[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=50000,b=50000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_ca[i] <- min(x[tmp < 0])
+}
+mean(flex_ca)
+sd(flex_ca)
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot() +
+    geom_point(aes(x=1:m, y=flex_ca), color="#d33636") +
+    geom_hline(yintercept=mean(flex_ca), color="#d33636", linetype="dashed", size=1.5) + 
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure V: Scatter Plot of MC Cases Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
+#plot(cs)
+ggplot(italy, aes(x = days, y = total_cases)) + 
+    geom_point() + 
+    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure VI: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases") + 
+  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
+```
+
+The mean of the day of flex for cases is 40.59 days and the standard deviation is 5.222832 days.
+
+In figure V,each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations.
+
+### MonteCarlo Simulation for Cumulative Fatalities of COVID-19 in Italy
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+# fatalities
+flex_fa <- rep(NA, m)
+for (i in 1:m) {
+  per_m <- model_fa[i, ]
+  model_try <-nlsLM(per_m ~ gauss_fn(days, a, b, c, d),
+                  data = italy_mod,
+                  start = list(a=15000,b=15000,c=.01,d=1))
+  get_coef <- summary(model_try)$parameters
+  get_coef <- get_coef[, 1]
+  names(get_coef) <- NULL
+  # Derivative of Gauss Error Function: 2 / sqrt(pi) * exp(-x ^ 2)
+  fn_try_deriv <-
+    bquote(.(get_coef[2]) * 2 / sqrt(pi) * exp(-(.(get_coef[3]) * x - .(get_coef[4])) ^ 2))
+  fn_try_deriv <- D(fn_try_deriv, 'x')
+  x = seq(1, 67, length.out = 6700)
+  tmp <- eval(fn_try_deriv)
+  flex_fa[i] <- min(x[tmp < 0])
+}
+flex_fa <- flex_fa[-c(12,112,124,133)]
+mean(flex_fa)
+sd(flex_fa)
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+ggplot() +
+    geom_point(aes(x=1:146, y=flex_fa), color="#1b95ff") +
+    geom_hline(yintercept=mean(flex_fa), color="#1b95ff", linetype="dashed", size=1.5) + 
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure VII: Scatter Plot of MC Fatality Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
+#plot(ft)
+ggplot(italy, aes(x = days, y = total_deaths)) +
+    geom_point() +
+    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
+    scale_x_continuous(breaks = seq(0, 67, 10)) +
+    theme(title =element_text(size=6)) +
+    labs(title = "Figure VIII: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths") +
+  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
+```
+
+The mean of the day of flex for fatalities is 43.46 days and the standard deviation is 5.228381 days.
+As you can see, the variance is high for both cases data and fatality data, an assumption might be because of smaller sample size.
 

### 2022-12-14 paper.rmd
updatepaper

@@
 
-# Introduction (Should we do an Abstract?)
+# Introduction
 
@@
 
-*Insert text here*
+## Available Official Data (Positive Cases)
 
-# Chien: Italy
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
+# extract China data of interest
+china <- data |>
+  filter(location == "China") |>
+  filter(date >= "2020-01-22", date <= "2020-03-28") |>
+  select(c(date, total_cases, total_deaths)) |>
+  mutate(days = 1:n())
+
+# recreate plots
+positive <- ggplot(data = china) +
+  geom_point(aes(x = date, y = total_cases)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Date", y = "China cumulative number of cases")
+positive
+```
+
+## Available Official Data (Fatalities)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
+ggplot(data = china) +
+  geom_point(aes(x = date, y = total_deaths)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Date", y = "China cumulative number of fatalities") +
+  ylim(0,5000)
+```
+
+## Fit by the Gauss Error Function
+
+Apply an $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.
+
+```{r, include=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+```
+
+```{r, message=FALSE, warning=FALSE}
+model <- nls(total_cases ~ gauss_fn(days,a,b,c,d), 
+             data=china, 
+             start=list(a=10000,b=10000,c=0.1,d=1))
+```
+
+## Fit by the Gauss Error Function and Peak Day (Positive Cases)
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+try <- china$total_cases
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+peak1 <- min(x[tmp < 0])
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+# summary(model1)$parameters
+fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_cases)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Days", y = "China cumulative number of cases") +
+  stat_function(fun=fn_model1, color="#d33636", size=1.5) +
+  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
+```
+
+## Fit by the Gauss Error Function and Peak Day (Fatalities)
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+try <- china$total_deaths
+model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
+est_try <- summary(model_try)$parameters
+est_try <- est_try[, 1]
+names(est_try) <- NULL
+fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+
+# find the second derivative of fitted function
+# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
+erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+fn_try_deriv <- D(fn_try_deriv,'x')
+x=seq(1,67,length.out=6700)
+tmp <- eval(fn_try_deriv)
+peak2 <- min(x[tmp < 0])
+```
+
+```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+#summary(model2)$parameters
+fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_deaths)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Days", y = "China cumulative number of fatalities") +
+  ylim(0,5000) +
+  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
+  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
+```
+
+# Italy
 

### 2022-12-14 chien_sim.Rmd

--- 2022-12-05 chien_sim.Rmd
@@
 
-## Day of flex (trial)
+## Day of flex (test)
 
 ```{r}
-# trial 1
-test <- model_fa[11,]
-model_try <- nlsLM(test ~ gauss_fn(days,a,b,c,d), 
-                 data=italy_mod, 
-                 start=list(a=50000,b=50000,c=.01,d=1))
-est_try <- summary(model_try)$parameters
-est_try <- est_try[, 1]
-names(est_try) <- NULL
-# fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
-
-erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
-
-fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
-fn_try_deriv <- D(fn_try_deriv,'x')
-x=seq(1,67,length.out=6700)
-tmp <- eval(fn_try_deriv)
-min(x[tmp < 0])
+# test <- model_fa[11,]
+# model_try <- nlsLM(test ~ gauss_fn(days,a,b,c,d), 
+#                  data=italy_mod, 
+#                  start=list(a=50000,b=50000,c=.01,d=1))
+# est_try <- summary(model_try)$parameters
+# est_try <- est_try[, 1]
+# names(est_try) <- NULL
+# # fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
+# 
+# erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
+# 
+# fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
+# fn_try_deriv <- D(fn_try_deriv,'x')
+# x=seq(1,67,length.out=6700)
+# tmp <- eval(fn_try_deriv)
+# min(x[tmp < 0])
 ```
 
-##
+## Day of flex
 
@@
     geom_point() + 
-    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
+    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
     labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
-  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")
+  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
 
@@
     geom_point() + 
-    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
+    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
     scale_x_continuous(breaks = seq(0, 67, 10)) +
     labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") + 
-  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
+  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
 ```

### 2022-12-15 paper.rmd
Added China portion of paper

@@
 
-In our MonteCarlo simulation analysis, we fit a gauss-error function over cumulaative Covid-19 data.
+In our MonteCarlo simulation analysis, we fit a gauss-error function over cumulative Covid-19 data.
 In the study mentioned below, the authors stated that it is widely accepted that China's Covid-19 data follows a gauss-error function. 
@@
 
-The authors perfomed a MonteCarlo simulation with 150 replications to approximate the day of flex point for China and Italy.
+The authors performed a MonteCarlo simulation with 150 replications to approximate the day of flex point for China and Italy.
 The use of the MonteCarlo simulation was crucial to their study's success as reported cases and fatalities can differ up `to 10%` from the actual number of cases and fatalities.
 
-# Jin: China
+# China
 
-## Available Official Data (Positive Cases)
+## Preview of the Data
+
+In Ciufolini and Paolozzi's MonteCarlo Study, the authors stated that it is widely accepted that China's Covid-19 data follows a gauss-error function.
+To confirm that, we first used the China data from January 22, 2020 (included), to March 27, 2020 (included) to take a look.
+The figures below are the cumulative number of diagnosed positive cases of COVID-19 in China and the cumulative number of fatalities due to COVID-19 in China.
 
@@
 
-## Available Official Data (Fatalities)
-
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
@@
 
-## Fit by the Gauss Error Function
+## Gauss Error Function
 
-Apply an $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.
+In the study, to fit the data, the authors stated that they used a function of the type of the Gauss error function, that is, the integral of a normal, Gaussian distribution: 
+$$a+b*erf(c*x-d)$$ 
+There are four parameters $a,b,c,d$ in this model, which shows great level of fit.
+Since they didn't specify how to realize the function in R, we went around and found that the $nls$ function did a great job on what we need.
+We took a cheap gauss of $a,b,c,d$ from the preview of the data as the start points, and apply the $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$.
+Here is an example code of the model construction by the $nls$ function:
 
@@
 
-## Fit by the Gauss Error Function and Peak Day (Positive Cases)
+## Fitting a Gauss Error Function to China's Data
+
+In this section, we reported the results of the fit of China's data.
+The figures below are the fit of the cumulative number of diagnosed positive cases of COVID-19 in China and the fit of the cumulative number of fatalities due to COVID-19 in China.
+The red solid lines are the fitting functions of the type of a Guass error function with four parameters.
+The horizontal axis shows the day numbers from January 22, 2020 (included), to March 27, 2020 (included).
+The vertical axis shows the cumulative numbers.
 
@@
 
-## Fit by the Gauss Error Function and Peak Day (Fatalities)
-
 ```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
+We can tell that both fitting function fit the cumulative number dots pretty well, which verified the study's saying that China's Covid-19 data follows a gauss-error function.
+
+## China's Day of Flex
 

### 2022-12-15 paper.rmd
Added China portion of paper

@@
   pdf_document:
-    toc: TRUE
+    toc: yes
     toc_depth: 2
-    number_sections: TRUE
+    number_sections: yes
     df_print: paged
-    fig_caption: TRUE
+    fig_caption: yes
     highlight: tango
+  html_document:
+    toc: yes
+    toc_depth: '2'
+    df_print: paged
 ---
@@
 positive
-```
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
 ggplot(data = china) +
@@
 $$a+b*erf(c*x-d)$$
+
 There are four parameters $a,b,c,d$ in this model, which shows great level of fit.
@@
 The red solid lines are the fitting functions of the type of a Guass error function with four parameters. 
-The horizontal axis shows the day numbers from January 22, 2020 (included), to March 27, 2020 (included).
-The vertical axis shows the cumulative numbers.
+The horizontal axis shows the day numbers from January 22, 2020 (included), to March 27, 2020 (included). The vertical axis shows the cumulative numbers.
 
@@
   labs(x = "Days", y = "China cumulative number of cases") +
-  stat_function(fun=fn_model1, color="#d33636", size=1.5) +
-  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
-```
+  stat_function(fun=fn_model1, color="#d33636", size=1.5)
 
-```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
 try <- china$total_deaths
@@
 peak2 <- min(x[tmp < 0])
+
+model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+#summary(model2)$parameters
+fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_deaths)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Days", y = "China cumulative number of fatalities") +
+  ylim(0,5000) +
+  stat_function(fun=fn_model2, color="#1b95ff", size=1.5)
 ```
 
+We can tell that both fitting function fit the cumulative number dots pretty well, which verified the study's saying that China's Covid-19 data follows a gauss-error function.
+
+## China's Day of Flex
+
+The day of flex is the peak day of daily cases, that is, the day that the second derivative of the fit of cumulative number changes sign, from acceleration to deceleration. 
+To analyze the day of flex of positive cases and fatalities in China, we took the second derivative of the Gauss error function we fitted above, and used the first day with negative second derivative as the day of flex.
+The red dashed vertical line shows the day of flex.
+
 ```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
+model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
+# summary(model1)$parameters
+fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
+ggplot(data = china) +
+  geom_point(aes(x = days, y = total_cases)) +
+  theme(title =element_text(size=6)) +
+  labs(x = "Days", y = "China cumulative number of cases") +
+  stat_function(fun=fn_model1, color="#d33636", size=1.5)
+
 model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
@@
 
-We can tell that both fitting function fit the cumulative number dots pretty well, which verified the study's saying that China's Covid-19 data follows a gauss-error function.
-
-## China's Day of Flex
+The day of flex of cumulative number of diagnosed positive cases in China is 18.66 and the day of flex of cumulative number of fatalities in China is 24.74. 
+We can tell that they are both around the middle of the climbing portion of the data, where the cumulative number starts to decelerate in growing.
 

### 2022-12-15 paper.rmd

@@
 In the study, to fit the data, the authors stated that they used a function of the type of the Gauss error function, that is, the integral of a normal, Gaussian distribution:
+
 $$a+b*erf(c*x-d)$$

### 2022-12-15 paper.rmd

@@
 
-# Austin: Australia
+# Australia
 
@@
     theme(title =element_text(size=6)) + 
-    labs(title = "Figure A: Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+    labs(title = "Figure A: Total Cases in Australia from 6/2/2020 \n to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
 fatalities_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
@@
     theme(title =element_text(size=6)) + 
-    labs(title = "Figure B: Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+    labs(title = "Figure B: Total Deaths in Australia from 6/2/2020 \n to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
 ```
@@
     scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
-    labs(title = "Figure C: Total Cases in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
+    labs(title = "Figure C: Total Cases in Australia from 6/2/2020 \n to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
 fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
@@
     scale_x_continuous(breaks = seq(0, minimizedDays, 10)) +
-    labs(title = "Figure D: Total Deaths in Australia from 6/2/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
+    labs(title = "Figure D: Total Deaths in Australia from 6/2/2020 \n to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
 ```
@@
     scale_x_continuous(breaks = seq(0, 200, 10)) +
-    labs(title = "Total Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+    labs(title = "Total Cases in Australia from 6/2/2020  \n to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
 fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
@@
     scale_x_continuous(breaks = seq(0, 200, 10)) +
-    labs(title = "Total Deaths in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+    labs(title = "Total Deaths in Australia from 6/2/2020  \n to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
 ```
@@
     xlim(0, 200) +
-    labs(title = "Figure E: Extrapolating Future Case Data with Gauss Error Function", x = "Days", y = "Total Cases")
+    labs(title = "Figure E: Extrapolating Future Case Data with \n Gauss Error Function", x = "Days", y = "Total Cases")
 fatalities_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
@@
     xlim(0, 200) +
-    labs(title = "Figure F: Extrapolating Future Fatality Data with Gauss Error Function", x = "Days", y = "Total Deaths")
+    labs(title = "Figure F: Extrapolating Future Fatality Data with \n Gauss Error Function", x = "Days", y = "Total Deaths")
 ```
@@
     stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
-    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    scale_x_continuous(breaks = seq(0, 200, 50)) +
     geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") +
-    labs(title = "Figure K: Entire Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
+    labs(title = "Figure K: Entire Cases in Australia from 6/2/2020 \n to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
 fatalities_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_deaths)) +
@@
     stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
-    scale_x_continuous(breaks = seq(0, 200, 10)) +
+    scale_x_continuous(breaks = seq(0, 200, 50)) +
     geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
-    labs(title = "Figure L: Entire Fatalities in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
+    labs(title = "Figure L: Entire Fatalities in Australia from 6/2/2020 \n to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
 ```
@@
 us_data_cases <- ggplot(data=us, aes(x=days, y=total_cases, color=year)) + 
-  geom_point() + 
-  labs(title="Figure M: Total Cases in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
+  geom_point() + theme(legend.position="top") + 
+  theme(title =element_text(size=6)) + 
+  labs(title="Figure M: Total Cases in the United States from 1/22/2020 \n to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
 us_data_deaths <- ggplot(data=us, aes(x=days, y=total_deaths, color=year)) + 
-  geom_point() + 
-  labs(title="Figure N: Total Deaths in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
+  geom_point() + theme(legend.position="top") + 
+  theme(title =element_text(size=6)) + 
+  labs(title="Figure N: Total Deaths in the United States from 1/22/2020 \n to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
 ```

### 2022-12-15 paper.rmd
Added china figures titles

@@
   theme(title =element_text(size=6)) +
-  labs(x = "Date", y = "China cumulative number of cases")
+  labs(title = "Figure 1: Total Cases in China from 1/22/2020 to 3/27/2020",
+       x = "Date", y = "China cumulative number of cases")
 positive
@@
   theme(title =element_text(size=6)) +
-  labs(x = "Date", y = "China cumulative number of fatalities") +
+  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 to 3/27/2020",
+       x = "Date", y = "China cumulative number of fatalities") +
   ylim(0,5000)
@@
   theme(title =element_text(size=6)) +
-  labs(x = "Days", y = "China cumulative number of cases") +
+  labs(title = "Figure 3: Total Cases in China with Gauss Error Function",
+       x = "Days", y = "China cumulative number of cases") +
   stat_function(fun=fn_model1, color="#d33636", size=1.5)
@@
   theme(title =element_text(size=6)) +
-  labs(x = "Days", y = "China cumulative number of fatalities") +
+  labs(title = "Figure 4: Total Deaths in China with Gauss Error Function",
+       x = "Days", y = "China cumulative number of fatalities") +
   ylim(0,5000) +
@@
   theme(title =element_text(size=6)) +
-  labs(x = "Days", y = "China cumulative number of cases") +
+  labs(title = "Figure 5: Total Cases in China with Day of Flex",
+       x = "Days", y = "China cumulative number of cases") +
   stat_function(fun=fn_model1, color="#d33636", size=1.5)
@@
   theme(title =element_text(size=6)) +
-  labs(x = "Days", y = "China cumulative number of fatalities") +
+  labs(title = "Figure 6: Total Deaths in China with Day of Flex",
+       x = "Days", y = "China cumulative number of fatalities") +
   ylim(0,5000) +

### 2022-12-15 paper.rmd
update\n

@@
   theme(title =element_text(size=6)) +
-  labs(title = "Figure 1: Total Cases in China from 1/22/2020 to 3/27/2020",
+  labs(title = "Figure 1: Total Cases in China from 1/22/2020 \nto 3/27/2020",
        x = "Date", y = "China cumulative number of cases")
@@
   theme(title =element_text(size=6)) +
-  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 to 3/27/2020",
+  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 \nto 3/27/2020",
        x = "Date", y = "China cumulative number of fatalities") +
@@
   theme(title =element_text(size=6)) +
-  labs(title = "Figure 3: Total Cases in China with Gauss Error Function",
+  labs(title = "Figure 3: Total Cases in China with \nGauss Error Function",
        x = "Days", y = "China cumulative number of cases") +
@@
   theme(title =element_text(size=6)) +
-  labs(title = "Figure 4: Total Deaths in China with Gauss Error Function",
+  labs(title = "Figure 4: Total Deaths in China with \nGauss Error Function",
        x = "Days", y = "China cumulative number of fatalities") +
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure I: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
+    labs(title = "Figure I: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases")
 #plot
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure II: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
+    labs(title = "Figure II: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths")
 ```
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure III: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
+    labs(title = "Figure III: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases")
 #plot
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure IV: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
+    labs(title = "Figure IV: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths")
 ```
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure VI: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases") + 
+    labs(title = "Figure VI: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases") + 
   geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
@@
     theme(title =element_text(size=6)) +
-    labs(title = "Figure VIII: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths") +
+    labs(title = "Figure VIII: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths") +
   geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
